On the presentation of orthogonal groups over polynomial rings

### 2019-05-17 dl-paper.tex
Fixed Andrei's remarks

The following lemma summarizes basic properties of structure constants used in the computations below.
\begin{lemma} Suppose $\alpha, \beta \in \Phi$ are such that $\alpha+\beta \in \Phi$.
\begin{enumerate}\label{lem:structure-constants}
 \item $N_{\alpha, \beta} = -N_{\beta,\alpha}$;
 \item $N_{\alpha, \beta} = - N_{-\alpha, -\beta}$;
 \item $N_{\alpha, \beta} = N_{\beta, -\alpha-\beta} = N_{-\alpha-\beta, \alpha}.$
\end{enumerate}
\end{lemma}
\begin{proof} See~\cite[\S~14]{VP}. \end{proof}

@@

\begin{lemma}\label{Zrels} The elements $z_\alpha(s, \xi)$ satisfy the following relations for all $\xi, \eta\in A$, $s\in I$:
\begin{enumerate} 
\item\label{Z1} $z_{\alpha}(s, \xi) ^ {x_{-\alpha}(\eta)} = z_{\alpha}(s, \xi + \eta)$;
\item\label{Z2} $z_{\beta}(s, \xi) ^ {x_{-\alpha}(\eta)} = x_{-\alpha} (- s\xi \eta) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot s\eta)     \cdot z_{\beta}(s, \xi)\ \text{if}\ \alpha - \beta \in \Phi$;
\item\label{Z3} $z_{\beta}(s, \xi) ^ {x_{-\alpha}(\eta)} = x_{-\alpha} (s\xi \eta) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot s\xi^2\eta) \cdot z_{\beta}(s, \xi)\ \text{if}\ \alpha + \beta \in \Phi$;
\item\label{Z4} $z_{\beta}(s, \xi) ^ {x_{-\alpha}(\eta)} = z_{\beta}(s, \xi)\ \text{if}\ \alpha\perp\beta$;
\item\label{Z5} If $\alpha+\beta\in\Phi$, then holds:
\begin{multline} \nonumber z_{\alpha+\beta}(s\eta, \xi) = x_\alpha(\epsilon s) x_{-\beta}(-s\xi) \cdot x_{\beta}(s\xi\eta^2) \cdot x_{\alpha+\beta}(s \eta) \cdot \\ \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta) \cdot
  x_{-\alpha}(-\epsilon s\xi^2\eta^2) \cdot x_{-\alpha-\beta}(- s \xi^2 \eta) \cdot z_{-\beta}(s\xi, -\eta)\text{ where $\epsilon = N_{\alpha,\beta}$.}\end{multline}
\end{enumerate} \end{lemma}
\begin{proof}
The first four assertions are contained in~\cite[Lemma~9]{S15}, so it remains to verify the last assertion.
Direct computation shows that
\begin{multline} \nonumber
  z_{\alpha+\beta}(s\eta, \xi) = [x_\alpha(\epsilon s)^{x_{-\alpha-\beta}(\xi)}, x_\beta(\eta)^{x_{-\alpha-\beta}(\xi)}] =
  [x_\alpha(\epsilon s) x_{-\beta}(-s\xi), x_{\beta}(\eta) x_{-\alpha}(\epsilon \xi\eta)] = \\ 
  = x_\alpha(\epsilon s) \cdot x_{-\beta}(-s\xi) \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta)^{x_{\beta}(-\eta)} \cdot z_{-\beta}(s\xi, -\eta)^{x_{-\alpha}(-\epsilon \xi\eta)},
\end{multline} 
and the required assertion follows from~\eqref{Z2}.
\end{proof}

\begin{comment}
For a subset of roots $S \subseteq \Phi$ denote by $\mathcal{Z}(S, R, I)$ the subset of $\overline{\St}(\Phi, R, I)$ consisting of the following two families of elements:
\begin{itemize}
 \item $x_\alpha(s)$, $\alpha \in \Phi$, $s\in I$;
 \item $z_\alpha(s, \xi)$, $\alpha \in S$, $s\in I$, $\xi \in R$.
\end{itemize}

\begin{lemma} \label{weak-Stepanov} For any $\Phi$ of rank $\geq 2$ the set $\mathcal{Z}(\Phi, R, I)$ generates $\overline{\St}(\Phi, R, I)$ as a group.
 Further, if $\Phi$ is simply laced $\overline{\St}(\Phi, R, I)$ is generated by even smaller set $\mathcal{Z}(\Phi\setminus\{\alpha, \beta\}, R, I)$, 
  where $\alpha, \beta \in \Phi$ are arbitrary roots of $\Phi$. \end{lemma}
\begin{proof}
 The first assertion is well-known, see the first part of~\cite[Lemma~4]{S15}.
 Notice that it follows from relation~\eqref{Z5} that $\mathcal{Z}(S, R, I)$ generates the same group as $\mathcal{Z}(S \cup (S - S), R, I)$.
 The second assertion then follows from the first one and the fact that for $S := \Phi \setminus \{ \alpha, \beta \}$ one has $S \cup (S - S) = \Phi$.
\end{proof}
{\bf TODO:} Probably, in the same fashion we could reprove Stepanov's theorem in the simply laced case.
\end{comment}

@@

{\bf TODO:} One can write analogue of~\eqref{Z5} in the nonsimply-laced case and the above argument still applies.

For the proof of the following lemma we will need the following variant of Hall--Witt identity:
\begin{equation} \label{HW-variant} [x, [ y, z]] = \left([[ x^{-1}, y^{-1}], z] ^ {x^{-1}} \cdot  [[ z^{-1}, x], y^{-1}] ^ {z^{-1}}\right)^{y^{-1}}.\end{equation}

\begin{lemma} \label{Crels}
The elements $c_\alpha(s, t)$ satisfy the following relations for all $s\in I,\ t\in J,\ \xi\in A$.
 \begin{enumerate}
  \item \label{C1} $[c_\beta(s, t), x_{-\alpha}(\xi)] = x_{-\alpha}(- st\xi) \cdot x_{\beta-\alpha}(N_{-\alpha,\beta}s^2t\xi)$ if $\alpha-\beta \in \Phi$;
  \item \label{C2} $[c_\beta(s, t), x_{-\alpha}(\xi)] = x_{-\alpha}(st\xi + s^2t^2\xi) \cdot x_{-\alpha-\beta}(N_{\alpha, \beta}st^2\xi)$ if $\alpha+\beta \in \Phi$;
  \item \label{C3} $[c_\beta(s, t), x_{-\alpha}(\xi)] = 1$ if $\alpha \perp \beta$;
  \item \label{C4} If $\alpha+\beta\in\Phi$ then holds:
  \[c_{\alpha+\beta}(s, t\xi) = [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2),\]
  where $\epsilon = N_{\alpha,\beta}$.
 \end{enumerate}
\end{lemma}
\begin{proof}
To verify~\eqref{C1} suppose $\alpha - \beta \in \Phi$ and compute
\begin{multline} \nonumber [c_{\beta}(s, t), x_{-\alpha}(\xi)]  = [x_{\beta}(s), x_{-\beta}(t)] [x_{-\beta}(t), x_{\beta}(s)\cdot x_{\beta-\alpha}(N_{-\alpha, \beta} s\xi)] = \\
 = {}^{x_\beta(s)}\![x_{-\beta}(t), x_{\beta-\alpha}(N_{-\alpha, \beta}s\xi)] = x_{-\alpha}(- st\xi) \cdot x_{\beta-\alpha}(N_{-\alpha,\beta}s^2t\xi). \end{multline}

Now suppose $\alpha+\beta \in \Phi$. From~\eqref{HW-variant} we obtain that \begin{multline} \nonumber
[x_{-\alpha}(\xi), [x_\beta(s), x_{-\beta}(t)]] = \\ 
= \left([[ x_{-\alpha}(-\xi), x_\beta(-s)], x_{-\beta}(t)] ^ {x_{-\alpha}(-\xi)} \cdot  [[ x_{-\beta}(-t), x_{-\alpha}(\xi)], x_\beta(-s)] ^ {x_{-\beta}(-t)}\right)^{x_\beta(-s)} =  \\ = [x_{-\beta-\alpha}(-N_{-\beta,-\alpha}t\xi), x_\beta(-s)] ^ {x_{-\beta}(-t) x_\beta(-s)} = x_{-\alpha}(-st\xi) ^ {x_{-\beta}(-t) x_\beta(-s)} = \\
= (x_{-\alpha-\beta}(-N_{\alpha, \beta}st^2\xi) \cdot x_{-\alpha}(-st\xi))^{x_\beta(-s)} = x_{-\alpha-\beta}(-N_{\alpha, \beta}st^2\xi) \cdot x_{-\alpha}(-st\xi - s^2t^2\xi),
\end{multline} which implies~\eqref{C2}.

Finally, relation~\eqref{C4} can be verified by the following direct computation, which involves identities~\eqref{HW-variant} and $[x, yz]^y = [y^{-1}, x] \cdot [x, z]$:
\begin{multline} \nonumber [x_{\alpha+\beta}(s), x_{-\alpha-\beta}(t\xi)] = [x_{\alpha+\beta}(s), [x_{-\alpha}(-\epsilon t), x_{-\beta}(\xi)]] = \\ 
= \left([[ x_{\alpha+\beta}(-s), x_{-\alpha}(\epsilon t)], x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s)} \cdot  [[ x_{-\beta}(-\xi), x_{\alpha+\beta}(s)], x_{-\alpha}(\epsilon t)] ^ {x_{-\beta}(-\xi)}\right)^{x_{-\alpha}(\epsilon t)} = \\
= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [ x_{\alpha}(\epsilon s\xi), x_{-\alpha}(\epsilon t)] ^ {x_{-\beta}(-\xi)x_{-\alpha}(\epsilon t)}  = \\
= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [ x_{\alpha}(\epsilon s\xi), x_{-\alpha}(\epsilon t) x_{-\alpha-\beta}(t\xi)] ^ {x_{-\alpha}(\epsilon t)} = \\
= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [x_{-\alpha}(-\epsilon t), x_{\alpha}(\epsilon s\xi)] \cdot [x_{\alpha}(\epsilon s\xi), x_{-\alpha-\beta}(t\xi)] = \\
= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2). \qedhere
\end{multline}

@@

\begin{lemma} \label{image-K-a-b} The image of $K(\alpha, \beta)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$  generated by $K(\alpha, \beta)$ and $Z_{\alpha, \beta}$. \end{lemma}
\begin{proof} To simplify notation we call the generators of the subgroup $Z_{\alpha,\beta}$ ``generators of type Z``. By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate to each generator $z_\gamma(Xf, \xi)$ of type 1 by $x_\alpha(aX^{-1})$ is a product of generators of type Z, Z, 1.
By~\eqref{eq:Zconj3} the conjugate to the generator $x_{-\alpha}(X^2f)$ is a product of generators of type 1, Z, 1, 2, 1, 1, Z, Z.
The conjugation by $x_\alpha(aX^{-1})$ fixes both generators of type 3 and transforms $x_{-\beta}(X^2f)$ into a products of generators of type 2, 1. As for the remaining generators of type 5, \cref{Crels} shows that the corresponding conjugate can be written as a product of generators of type Z, Z, 5. \end{proof}

@@

\begin{lemma} \label{conj-K-a-b} For $b \in A$ one has $K(\alpha, \beta)^{x_{\beta - \alpha}(b)} \subseteq K(\alpha, \beta)$. \end{lemma}
\begin{proof} By~\eqref{Z2}--\eqref{Z4} of~\cref{Zrels} the conjugate to the generator $g=z_\gamma(Xf, \xi)$ of type 1 by $x_{\beta-\alpha}(b)$ either coincides with $g$ or is a product of elements of type 4, 1, 1. Now if $g = x_\epsilon(Xf)$, $\epsilon \in \{\pm \alpha, \pm \beta\}$ is a generator of type 2 or 3, the conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of either two elements of type 2 or two elements of type 3. By~\eqref{C1}--\eqref{C3} of~\cref{Crels} the conjugate to a generator $g = c_\delta(f, X\xi)$ of type 5 either coincides with $g$ or is a product of generators of type 5, 4, 1. Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, b) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$. \end{proof}

>>>>

The following lemma summarizes basic properties of structure constants which will be used in the computations below, often without explicit reference.
\begin{lemma} Suppose $\alpha, \beta \in \Phi$ are such that $\alpha+\beta \in \Phi$.
\begin{enumerate}\label{lem:structure-constants}
 \item $N_{\alpha, \beta} = -N_{\beta,\alpha}$;
 \item $N_{\alpha, \beta} = - N_{-\alpha, -\beta}$;
 \item $N_{\alpha, \beta} = N_{\beta, -\alpha-\beta} = N_{-\alpha-\beta, \alpha}.$
\end{enumerate}
\end{lemma}
\begin{proof} See~\cite[\S~14]{VP}. \end{proof}

@@

\begin{lemma}\label{Zrels} The elements $z_\alpha(s, \xi)$ satisfy the following relations for all $\xi, \eta\in A$, $s\in I$:
\begin{enumerate} 
\item\label{Z1} $z_{\alpha}(s, \xi) ^ {x_{-\alpha}(\eta)} = z_{\alpha}(s, \xi + \eta)$;
\item\label{Z2} $z_{\beta}(s, \xi) ^ {x_{\alpha}(\eta)} = x_{\alpha} (- s\xi \eta) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot s\eta)     \cdot z_{\beta}(s, \xi)\ \text{if}\ \alpha + \beta \in \Phi$;
\item\label{Z3} $z_{\beta}(s, \xi) ^ {x_{\alpha}(\eta)} = x_{\alpha} (s\xi \eta) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot s\xi^2\eta) \cdot z_{\beta}(s, \xi)\ \text{if}\ \alpha - \beta \in \Phi$;

\item\label{Z4} $z_{\beta}(s, \xi) ^ {x_{\alpha}(\eta)} = z_{\beta}(s, \xi)\ \text{if}\ \alpha\perp\beta$;
\item\label{Z5} If $\alpha+\beta\in\Phi$, then holds:
\begin{multline} \nonumber z_{\alpha+\beta}(s\eta, \xi) = x_\alpha(\epsilon s) x_{-\beta}(-s\xi) \cdot x_{\beta}(s\xi\eta^2) \cdot x_{\alpha+\beta}(s \eta) \cdot \\ \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta) \cdot
  x_{-\alpha}(-\epsilon s\xi^2\eta^2) \cdot x_{-\alpha-\beta}(- s \xi^2 \eta) \cdot z_{-\beta}(s\xi, -\eta)\text{ where $\epsilon = N_{\alpha,\beta}$.}\end{multline}
\end{enumerate} \end{lemma}
\begin{proof}
The first four assertions are contained in~\cite[Lemma~9]{S15}, so it remains to verify the last assertion.
Direct computation shows that
\begin{multline} \nonumber
  z_{\alpha+\beta}(s\eta, \xi) = [x_\alpha(\epsilon s)^{x_{-\alpha-\beta}(\xi)}, x_\beta(\eta)^{x_{-\alpha-\beta}(\xi)}] =
  [x_\alpha(\epsilon s) x_{-\beta}(-s\xi), x_{\beta}(\eta) x_{-\alpha}(\epsilon \xi\eta)] = \\ 
  = x_\alpha(\epsilon s) \cdot x_{-\beta}(-s\xi) \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta)^{x_{\beta}(-\eta)} \cdot z_{-\beta}(s\xi, -\eta)^{x_{-\alpha}(-\epsilon \xi\eta)},
\end{multline} 
and the required assertion follows from~\eqref{Z2}.
\end{proof}

@@

For the proof of the following lemma we will need the following variant of Hall--Witt identity:
\begin{equation} \label{HW-variant} [[x, y], z] = \left([x^{-1}, [ y^{-1}, z]] ^ {y^{-1}} \cdot [y, [ z^{-1}, x^{-1}]] ^ {z^{-1}} \right)^{x^{-1}}.\end{equation}

\begin{lemma} \label{Crels}
The elements $c_\alpha(s, t)$ satisfy the following relations for all $s\in I,\ t\in J,\ \xi\in A$.
 \begin{enumerate}
 \item \label{C1} $[c_\beta(s, t), x_{\alpha}(\xi)] = x_{\alpha}(- st\xi) \cdot x_{\beta+\alpha}(N_{\alpha,\beta}s^2t\xi)$ if $\alpha+\beta \in \Phi$;
 \item \label{C2} $[c_\beta(s, t), x_{\alpha}(\xi)] = x_{\alpha}(st\xi + s^2t^2\xi) \cdot x_{\alpha-\beta}(N_{-\alpha, \beta}st^2\xi)$ if $\alpha-\beta \in \Phi$;  
 \item \label{C3} $[c_\beta(s, t), x_{\alpha}(\xi)] = 1$ if $\alpha \perp \beta$;  
 \item \label{C4} If $\alpha+\beta\in\Phi$ then holds:
  \[c_{\alpha+\beta}(s, t\xi) = [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2),\]
  where $\epsilon = N_{\alpha,\beta}$.
 \end{enumerate}
\end{lemma}
\begin{proof}
To verify~\eqref{C1} suppose $\alpha + \beta \in \Phi$ and compute
\begin{multline} \nonumber [c_{\beta}(s, t), x_{\alpha}(\xi)]  = [x_{\beta}(s), x_{-\beta}(t)] \cdot [x_{-\beta}(t), x_{\beta}(s)\cdot x_{\beta+\alpha}(N_{\alpha, \beta} \cdot s\xi)] = \\
 = {}^{x_\beta(s)}\![x_{-\beta}(t), x_{\alpha+\beta}(N_{\alpha, \beta} \cdot s\xi)] = x_{\alpha}(- st\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta} \cdot s^2t\xi). \end{multline}

In the case $\alpha-\beta \in \Phi$ the second assertion directly follows from~\eqref{HW-variant}:
\begin{multline} \nonumber
[[x_\beta(s), x_{-\beta}(t)], x_{\alpha}(\xi)] = \\
= \left([x_\beta(-s), [ x_{-\beta}(-t), x_{\alpha}(\xi)]] ^ {x_{-\beta}(-t)} \cdot [x_{-\beta}(t), [ x_{\alpha}(-\xi), x_\beta(-s)]] ^ {x_{\alpha}(-\xi)}\right)^{x_\beta(-s)} = \\
= x_{\alpha}(-N_{\beta, \alpha-\beta} N_{\alpha,-\beta} \cdot s t \xi) ^ {x_{-\beta}(-t) \cdot x_\beta(-s)} = x_{\alpha}(s t \xi) ^ {x_{-\beta}(-t) \cdot x_\beta(-s)} = \\
= x_{\alpha}(st\xi) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot st^2\xi)^{x_\beta(-s)} = x_{\alpha}(st\xi + s^2t^2 \xi) \cdot x_{\alpha-\beta}(N_{-\alpha,\beta}\cdot st^2\xi). \end{multline}

Finally, the final relation can be verified by the following direct computation, which involves identity $[x, yz]^y = [y^{-1}, x] \cdot [x, z]$ and \eqref{HW-variant} with both sides of the equation inverted:
\begin{multline} \nonumber [x_{\alpha+\beta}(s), x_{-\alpha-\beta}(t\xi)] = [x_{\alpha+\beta}(s), [x_{-\alpha}(-\epsilon t), x_{-\beta}(\xi)]] = \\ 
= \left([[ x_{\alpha+\beta}(-s), x_{-\alpha}(\epsilon t)], x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s)} \cdot  [[ x_{-\beta}(-\xi), x_{\alpha+\beta}(s)], x_{-\alpha}(\epsilon t)] ^ {x_{-\beta}(-\xi)}\right)^{x_{-\alpha}(\epsilon t)} = \\
= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [ x_{\alpha}(\epsilon s\xi), x_{-\alpha}(\epsilon t)] ^ {x_{-\beta}(-\xi)x_{-\alpha}(\epsilon t)}  = \\
= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [ x_{\alpha}(\epsilon s\xi), x_{-\alpha}(\epsilon t) x_{-\alpha-\beta}(t\xi)] ^ {x_{-\alpha}(\epsilon t)} = \\
= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [x_{-\alpha}(-\epsilon t), x_{\alpha}(\epsilon s\xi)] \cdot [x_{\alpha}(\epsilon s\xi), x_{-\alpha-\beta}(t\xi)] = \\
= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2). \qedhere
\end{multline}

@@

\begin{lemma} \label{image-K-a-b} The image of $K(\alpha, \beta)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$  generated by $K(\alpha, \beta)$ and $Z_{\alpha, \beta}$. \end{lemma}
\begin{proof} To simplify notation we call the generators of the subgroup $Z_{\alpha,\beta}$ ``generators of type Z``. By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate to each generator $z_\gamma(Xf, \xi)$ of type 1 by $x_\alpha(aX^{-1})$ is a product of generators of type Z, Z, 1.
By~\eqref{eq:Zconj3} the conjugate to the generator $x_{-\alpha}(X^2f)$ is a product of generators of type 1, Z, 1, 2, 1, 1, Z, Z.
The conjugation by $x_\alpha(aX^{-1})$ fixes both generators of type 3 and transforms $x_{-\beta}(X^2f)$ into a product of generators of type 2, 1. As for the remaining generators of type 5, \cref{Crels} shows that the corresponding conjugate can be written as a product of generators of type Z, Z, 5. \end{proof}

@@

\begin{lemma} \label{conj-K-a-b} For $b \in A$ one has $K(\alpha, \beta)^{x_{\beta - \alpha}(b)} \subseteq K(\alpha, \beta)$. \end{lemma}
\begin{proof} By~\eqref{Z2}--\eqref{Z4} of~\cref{Zrels} the conjugate to the generator $g=z_\gamma(Xf, \xi)$ of type 1 by $x_{\beta-\alpha}(b)$ either coincides with $g$ or is a product of generators of type 4, 1, 1. Now if $g = x_\epsilon(Xf)$, $\epsilon \in \{\pm \alpha, \pm \beta\}$ is a generator of type 2 or 3, the conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of two generators of type 2 or 3. By~\eqref{C1}--\eqref{C3} of~\cref{Crels} the conjugate to a generator $g = c_\delta(f, X\xi)$ of type 5 either coincides with $g$ or is a product of generators of type 5, 4, 1. Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, b) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$. \end{proof}
